\documentclass[11pt,a4paper]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{enumitem}

\title{GEODATACENTER PHASE 1}
\author{UBOS Constitutional AI}
\date{2025-08-01}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Excellence}
# Excellence Narrative


## Objectives and Ambition
- Deliver GeoDataCenter Phase 1 aligned with HORIZON-2025-GEOTHERMAL-01.
- Harness UBOS constitutional AI governance for transparent, human-centred deployment.
- Demonstrate innovation via Oracle Trinity integration and sovereign infrastructure.



\section{Impact}
# Impact Narrative


## Impact Pathway
- Economic: Expected to unlock €70M across consortium regions.
- Social: Benefits European SMEs through co-designed services.
- Environmental: Supports EU Green Deal via geothermal-powered compute.

## Measures to Maximise Impact
- Communication: Monthly COMMS_HUB updates plus partner newsletters.
- Exploitation: Joint IP committee chaired by the UBOS Treasury Administrator.
- Open Science: Data management plan ensuring FAIR datasets (with farmer consent safeguards).



\section{Implementation}
# Implementation Narrative


## Work Plan Overview
- WP1: Intelligence & Research (UBOS lead, Months 1-6).
- WP2: Development & Deployment (Consortium, Months 4-18).
- WP3: Validation & Demonstration (User partners, Months 10-22).
- WP4: Dissemination & Exploitation (All partners, Months 6-24).

## Governance
- Mode Beta supervisory loop keeps humans-in-the-loop for high-risk actions.
- Treasury Cascade enforces constitutional budgeting across work packages.
- Emergency stop procedures integrated with partner operations and EU ethics guidance.



\section{Work Plan Summary}
# GRANT ASSEMBLY WORKFLOW: GeoDataCenter Phase 1

**Opportunity:** HORIZON-2025-GEOTHERMAL-01
**Deadline:** 2025-09-02T17:00:00+00:00
**Fit Score:** 4.3
**Budget Target:** €5,000,000-€10,000,000
**Assembly Start:** 2025-10-30
**Estimated Completion:** 2025-12-14

## Phase 1: Intelligence Gathering
- [ ] Load EU Grant Hunter brief and call documentation
- [ ] Map UBOS capabilities to evaluation criteria
- [ ] Identify partner requirements and capability gaps
- [ ] Draft initial risk register

## Phase 2: Narrative Compilation
- [ ] Generate excellence narrative (Financial Proposal Generator)
- [ ] Generate impact narrative
- [ ] Generate implementation narrative (work plan, Mode Beta oversight)
- [ ] Constitutional alignment review (Lion's Sanctuary)

## Phase 3: Budget Assembly
- [ ] Define work packages and person-months
- [ ] Allocate costs per EU rules (direct/indirect)
- [ ] Validate UBOS internal allocations with Treasury Administrator
- [ ] Produce budget tables (CSV + markdown)

## Phase 4: Partner Coordination
- [ ] Dispatch commitment letter templates
- [ ] Track signatures (TBD partners)
- [ ] Collect CVs and organisation profiles
- [ ] Final consortium coordination call

## Phase 5: Compliance Checks
- [ ] Ethics & GDPR checklist
- [ ] Open science/data management plan
- [ ] Gender & diversity statement
- [ ] Sustainability alignment (EU Green Deal)
- [ ] Format validation (page limits, fonts, annexes)

## Phase 6: Packaging & Submission
- [ ] Merge narratives + budget into LaTeX template
- [ ] Run scoring simulator (target ≥4.6/5)
- [ ] Final quality review (Trinity approval)
- [ ] Submit ≥5 days before deadline (EU portal)
- [ ] Notify Treasury + update pipeline state

## Risk Log
| Risk | Likelihood | Impact | Mitigation | Owner |
|------|------------|--------|------------|-------|
| Partner dropout | Medium | High | Maintain backup candidates | Consortium Lead |
| Schedule slip | Medium | Critical | Weekly cadence, 5-day buffer | Assembly Coordinator |
| Budget rejection | Low | Medium | Treasury validation + EU template | Financial Officer |

## Notes
- Rapid mode compresses phases into 72 hours; document trade-offs explicitly.
- All partner communications logged via COMMS_HUB (grant_assembly channel).


\section{Budget Overview}
| Work Package | Share % | Direct (€) | Indirect (€) | Total (€) |
|---|---|---|---|---|
| WP1 - Research & Intelligence | 20.0 | 8,000,000.0 | 2,000,000.0 | 10,000,000.0 |
| WP2 - Development & Deployment | 35.0 | 14,000,000.0 | 3,500,000.0 | 17,500,000.0 |
| WP3 - Validation & Field Trials | 25.0 | 10,000,000.0 | 2,500,000.0 | 12,500,000.0 |
| WP4 - Dissemination & Management | 20.0 | 8,000,000.0 | 2,000,000.0 | 10,000,000.0 |


\appendix
\section{Partner Letters of Commitment}
See attached scanned letters.

\section{CVs of Key Personnel}
See attached CV bundle.

\section{Compliance Annex}
Compliance report stored in compliance/compliance_report.json

\end{document}
